---
title: "salamander linear model residuals"
output:  
  html_document:
    theme: readable
    css: !expr here::here("formatting", "css", "styles.css")
    toc: TRUE
    toc_float: TRUE
---


```{r, echo = FALSE, results = "hide", message=FALSE} 
# source(here::here("formatting", "functions", "rmd_functions.R"))
source(here::here("rmd_tools", "find_file.R"))
dat_dispersal = read.csv(find_file("salamander_dispersal.csv"))
# Calculates the value of x for a linear function, given the coordinates
# of a known point (x1, y1) and the slope of the line.
line_point_slope = function(x, x1, y1, slope)
{
  get_y_intercept = 
    function(x1, y1, slope) 
      return(-(x1 * slope) + y1)
  
  linear = 
    function(x, yint, slope) 
      return(yint + x * slope)
  
  return(linear(x, get_y_intercept(x1, y1, slope), slope))
}
```


Question
========

```{r CSS, echo = FALSE, results = "asis"}
cat(readLines(here::here("formatting", "css", "styles.css")))
```


> Recall the function we have used to visually estimate linear model parameters:

```{r}
# Calculates the value of x for a linear function, given the coordinates
# of a known point (x1, y1) and the slope of the line.
line_point_slope = function(x, x1, y1, slope)
{
  get_y_intercept = 
    function(x1, y1, slope) 
      return(-(x1 * slope) + y1)
  
  linear = 
    function(x, yint, slope) 
      return(yint + x * slope)
  
  return(linear(x, get_y_intercept(x1, y1, slope), slope))
}
```


Instructions:

1. Using the parameters you chose for your linear fit, calculate the residuals and store them in a vector `resids_linear`.


<div class="questionborder">
### Questions

- Q1 (3 pts.) Paste the code you used to create `resids_linear`.
- Q1 (1 pts.) Upload an image file with a histogram of the residuals of your linear model.

</div>






