---
title: "salamander data scatterplot"
output:  
  html_document:
    theme: readable
    css: !expr here::here("formatting", "css", "styles.css")
    toc: TRUE
    toc_float: TRUE
---


```{r, echo = FALSE, results = "hide", message=FALSE} 
# source(here::here("formatting", "functions", "rmd_functions.R"))
source(here::here("rmd_tools", "find_file.R"))
dat_dispersal = read.csv(find_file("salamander_dispersal.csv"))

```


Question
========

```{r CSS, echo = FALSE, results = "asis"}
cat(readLines(here::here("formatting", "css", "styles.css")))
```

Instructions:

1. Read the salamander dispersal data into a `data.frame` called `dat_dispersal`.
2. Create a scatterplot of distance class and dispersal rate of first time breeding salamanders.


<div class="questionborder">
### Questions

- Q1 (1 pts.) Upload an image file with your scatterplot.  Make sure it has appropriate axis labels and title.
- Q2 (2 pts.) Describe, in nontechnical language, what is shown on the x-axis
- Q3 (2 pts.) Describe, in nontechnical language, what is shown on the y-axis

</div>






