---
title: "Bolker 1.4: Null Hypothesis"
output:  
  html_document:
    theme: readable
    css: !expr here::here("formatting", "css", "styles.css")
    # toc: TRUE
    # toc_float: TRUE
editor_options:
  chunk_output_type: console
---


```{r, echo = FALSE, results = "hide"} 
source(here::here("formatting", "functions", "rmd_functions.R"))
```


Question
========

```{r CSS, echo = FALSE, results = "asis"}
cat(readLines(here::here("formatting", "css", "styles.css")))
```

> The two species (actually the smallest- and largest-seeded species of a set of eight species) are Polyscias fulva (pol: seed mass < 0.01 g) and Pseudospondias microcarpa (psd: seed mass ≈ 50 g).


In Frequentist statistics, a null hypothesis often describes what we expect to see if the variables we care about have no *assiciation*.  It's what we would observe if the values in our data were due to *chance*.

In Frequentist statistics, we formulate an alternative hypothesis to capture what we actually think is important.  We analyze our data to assess whether we have *good evience* that we can reject the *null hypothesis* in favor of our *alternative hypothesis*.  Note that we never say we *accept* the alternative hypothesis!.


### Seed Predation

From the Bolker reading, we don't know much about the two species other than that their seeds have very different masses.

The description of the experiment in the reading did not describe any factor that might be *associated* with seed predation.  Simply asking whether seed predation rates are different without any context to the environment in which the plants live is not a very interesting.

<div class="questionborder">

Propose a factor that could contribute to differential seed predation, and formulate null and alternative hypotheses





### Question

- Think of a reason why seeds may have 
Bolker used a seed predation experiment to illustrate the statistical frameworks.


The primary question in his examples is: *Do seed predation rates vary among* species?

A ***null hypothesis*** is used in the Frequentist paradigm as a baseline against which to compare data.


<div class="questionborder">

### Question:

Describe a possible null hypothesis about the seed predation rates.

Paste your answer into the text entry box below.

</div>




Solution
========

The most obvious null is: "There is no difference in seed predation rates among species."


Meta-information
================
extitle: null hypotheses
extype: string
exsolution: nil
exname: exam name
exsection: section name
exextra[essay,logical]: TRUE
exextra[essay_format,character]: editor
exextra[essay_required,logical]: FALSE
exextra[essay_fieldlines,numeric]: 5
exextra[essay_attachments,numeric]: 1
exextra[essay_attachmentsrequired,logical]: TRUE
expoints: 2