---
title: "Ricker params"
output:  
  html_document:
    theme: readable
    css: !expr here::here("formatting", "css", "styles.css")
    toc: TRUE
    toc_float: TRUE
---


```{r, echo = FALSE, results = "hide", message=FALSE} 
require(rmd.utils)

ricker_fun = function(x, a, b) { return(a * x * exp(-b * x))}
```


Question
========

```{r CSS, echo = FALSE, results = "asis"}
cat(readLines(here::here("formatting", "css", "styles.css")))
```

Instructions:

1. To gain visual intuition, try using `curve()` to plot the Ricker function.
  - Try out different values of the two parameters as well as plotting over different ranges of x-values.
  - Try plotting two or more curves with slightly different parameter values on the same plot
  - You may need to try out different ranges of x-values in your plot windows to make sure you are focusing on the interesting parts of the curves.
  - Try different line colors, widths, and textures.

An example exploratory plotting exercise:

```{r echo=FALSE}
curve(ricker_fun(x, 25.1, .5), add = FALSE, from = 0, to = 10, ann = FALSE, ylab = "f(x)", ylim = c(0, 30)); box()
curve(ricker_fun(x, 20.2, .3), add = TRUE, col = 2)
curve(ricker_fun(x, 49.2, .66), add = TRUE, col = 3, lty = 2, lwd = 3)
curve(ricker_fun(x, 10.5, 0.8), add = TRUE, col = 4, lwd = 2)
# curve(ricker_fun(x, 1.75, 0.003), add = TRUE, from = 0, to = 100, col = 66, lwd = 3, lty = 4)

```




<div class="questionborder">
### Questions

- Q1 (2 pts.) Qualitatively describe how the `a` parameter influences the curve shape.
- Q2 (2 pts.) Qualitatively describe how the `b` parameter influences the curve shape.

</div>

<div class="hintborder"> NOTE: make sure you choose an appropriate range of x-values in your plot.</div>



Solution
========

```{r}
curve(ricker_fun(x, 25, 0.1), add = FALSE, from = 0, to = 50, ylab = "f(x)")
curve(ricker_fun(x, 20, 0.1), add = TRUE, col = 1, lty = 2)
curve(ricker_fun(x, 10, 0.1), add = TRUE, col = 1, lty = 2)
curve(ricker_fun(x, 75, 0.3), add = TRUE, col = 2, lty = 1)
curve(ricker_fun(x, 50, 0.3), add = TRUE, col = 2, lty = 2)
curve(ricker_fun(x, 40, 0.3), add = TRUE, col = 2, lty = 2)

```





Meta-information
================
extitle: Ricker params
extype: string
exsolution: nil
exname: lab 5
exsection: lab 5
exextra[essay,logical]: TRUE
exextra[essay_format,character]: noinline
exextra[essay_required,logical]: FALSE
exextra[essay_fieldlines,numeric]: 5
exextra[essay_attachments,numeric]: 1
exextra[essay_attachmentsrequired,logical]: TRUE
expoints: 4
