---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r eval=FALSE, echo=FALSE}
require(rmd.utils)
exams::exams2moodle(file = find_file("cloze_mixed.Rmd"), dir = here::here("example_moodle_questions"))
```

```{r data generation, echo = FALSE, results = "hide"}
## DATA
require(exams)

tol = 2


## QUESTION/SOLUTION
questions = solutions = explanations = rep(list(""), 6)
type = rep(list("schoice"), 6)


# Unimodal
questions[[1]] = c("unimodal", "bimodal", "flat", "periodic")
solutions[[1]] = c(TRUE, rep(FALSE, length(questions[[1]]) - 1)) 


# skew
questions[[2]] = c("right-skewed", "symmetric", "left-skewed", "leptokurtotic")
solutions[[2]] = c(TRUE, rep(FALSE, length(questions[[2]]) - 1)) 




# outliers
questions[[3]] = c("are", "are not")
solutions[[3]] = c(TRUE, rep(FALSE, length(questions[[3]]) - 1)) 



# upper quartile
questions[[4]] = ""
solutions[[4]] = explanations[[4]] = 75
type[[4]] = "num"


    

# lower quartile
questions[[5]] = ""
solutions[[5]] = explanations[[5]] = 50
type[[5]] = "num"



# mean R function
questions[[6]] = ""
solutions[[6]] = explanations[[6]] = "mean()"
type[[6]] = "string"


explanations[1:3] = lapply(solutions[1:3], function(x) ifelse(x, "True", "False"))

solutions[1:3] = lapply(solutions[1:3], function(x) exams::mchoice2string(x))

# if(any(explanations[4:6] < 0)) explanations[4:6] = lapply(
#   solutions[4:6], function(x) paste("$", x, "$", sep = ""))

```


Question
========

A Normal distribution is \#\#ANSWER1\#\#.

When the mean is greater than the median, a distribution is \#\#ANSWER2\#\#.

In a well-behaved data set there \#\#ANSWER3\#\# outliers.

The upper quartile of the numbers 1 - 100 is \#\#ANSWER4\#\#.

The median of the numbers 1 - 100 is \#\#ANSWER5\#\#.

The R function to calculate the arithmetic mean is \#\#ANSWER6\#\#.


```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(unlist(questions), markup = "markdown")
```


Solution
========

```{r solutionlist, echo = FALSE, results = "asis"}
exams::answerlist(paste(unlist(explanations), ".", sep = ""), markup = "markdown")
```


Meta-information
================
extype: cloze
exsolution: `r paste(solutions, collapse = "|")`
exclozetype: `r paste(type, collapse = "|")`
exname: Boxplot and histogram
extol: 0|0|0|`r tol`|`r tol`|0
exshuffle: true

